---
title: "ST558 Project 2"
author: Michael Evans
date: 7/3/2020
output: 
  rmarkdown::github_document:
    toc: true
params:
  #weekday: weekday
  weekday: "Monday"
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(caret)
library(gbm)
library(randomForest)
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
You should have an introduction section that describes the data, the purpose of your analysis, and the methods you’ll use (roughly - more detail can be given later in the document).

## Description of Data
You should briefly describe the data and the variables you have to work with (no need to discuss all of them, just the ones you want to use).

## Purpose of Analysis

## Methods

# Reading Data

## Initial Read
```{r reading_data, message = F}
#Read Data
news <- read_csv("OnlineNewsPopularity.csv")

#Add column that tells which weekday it is
news <- news %>%
    mutate(Weekday = case_when(weekday_is_monday ==  1 ~ 'Monday',
                               weekday_is_tuesday ==  1 ~ 'Tuesday',
                               weekday_is_wednesday ==  1 ~ 'Wednesday',
                               weekday_is_thursday ==  1 ~ 'Thursday',
                               weekday_is_friday ==  1 ~ 'Friday',
                               weekday_is_saturday ==  1 ~ 'Saturday',
                               weekday_is_sunday ==  1 ~ 'Sunday'))

#Get News for One Day
daily_news <- news %>% filter(Weekday == params$weekday) %>% 
  select(-(weekday_is_monday:weekday_is_sunday))
```

## Creating New Variables

```{r new_variables}
#Make Shares into Factor
daily_news$shares_1400 <- ifelse(daily_news$shares > 1400, 1, 0)
daily_news$shares_1400 <- as.factor(daily_news$shares_1400)

#Create Variable for Channel Type
daily_news <- daily_news %>%
    mutate(channel = case_when(data_channel_is_lifestyle ==  1 ~ 'Lifestyle',
                               data_channel_is_entertainment ==  1 ~ 'Entertainment',
                               data_channel_is_bus ==  1 ~ 'Bus',
                               data_channel_is_socmed ==  1 ~ 'SocMed',
                               data_channel_is_tech ==  1 ~ 'Tech',
                               data_channel_is_world ==  1 ~ 'World'))

#Replace NA Values with "None"
daily_news$channel <- daily_news$channel %>% replace_na("None")
```

## Select Variables

```{r get_variables}
#Select Variables
daily_news <-daily_news %>% select(n_tokens_title, n_tokens_content, num_hrefs:num_videos, shares_1400, channel)

#Make Factor
daily_news$channel <- as.factor(daily_news$channel)
```

## Split into Train/Test Data

```{r train_test}
#Split into Training and Testing Set
set.seed(321)
train <- sample(1:nrow(daily_news), size = nrow(daily_news) * 0.7)
test <- setdiff(1:nrow(daily_news), train)

#Subset data
daily_train <- daily_news[train, ]
daily_test <- daily_news[test, ]
```

# Summarizations
You should produce some basic (but meaningful) summary statistics about the training data you are working with. The general things that the plots describe should be explained but, since we are going to automate things, there is no need to try and explain particular trends in the plots you see (unless you want to try and automate that too!).

# Modeling

## Linear Model
```{r linear_model}
#First Model
glm_fit1 <- glm(shares_1400 ~ n_tokens_title + n_tokens_content + num_videos + channel, 
                data = daily_train, family = "binomial")

glm_fit1$aic

#Second Model
glm_fit2 <- glm(shares_1400 ~ n_tokens_title + n_tokens_content + num_videos, 
                data = daily_train, family = "binomial")
glm_fit2$aic
```

## Non-Linear Model

```{r bagged_tree}
#Create Model
bagged_tree <- train(shares_1400 ~ ., data = daily_train, method = "treebag",
                     trControl = trainControl(method = "cv"), tuneLength = 10)

#View Model
bagged_tree
```

# Modeling Results

## Linear Model

```{r linear_predict}
glm_pred1 <- predict(glm_fit1, newdata = daily_test)

#Round Output
glm_pred1 <- round(glm_pred1, 0)

#Make Data Frame
glm_pred1 <- data.frame(glm_pred1)
names(glm_pred1) <- "shares_1400"

#Adjust for Bounds
glm_pred1[,1][glm_pred1[,1] < 0] <- 0
glm_pred1[,1][glm_pred1[,1] > 1] <- 1

#Create Levels
levels(glm_pred1$shares_1400) <- c("0", "1")

#Make Factor
glm_pred1$shares_1400 <- as.factor(glm_pred1$shares_1400)

#Create Confusion Matrix
matrix1 <- confusionMatrix(glm_pred1$shares_1400, daily_test$shares_1400)
matrix1
```

## Non-Linear Model

```{r predict_bagged}
#Predict Bagged Tree
bagged_pred <- predict(bagged_tree, daily_test)

#Create Results
bagged_results <- confusionMatrix(data = bagged_pred, reference = daily_test$shares_1400)
bagged_results
```

# Conclusion

