---
title: "ST558 Project 2"
author: Michael Evans
date: 7/3/2020
output: 
  rmarkdown::github_document:
    toc: true
params:
  weekday: weekday
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(caret)
library(gbm)
library(randomForest)
knitr::opts_chunk$set(echo = TRUE)
```

# Code to Render File for Each Day of the Week

```{r render_day, eval = F}
#Create Function to Render File
render_function <- function(day){
  rmarkdown::render(
  "Project_Work.Rmd", 
  params = list(weekday = day),
  output_file = paste0(day,"-", "Report", ".md")
)
}

#Create Vector of Days of the Week
days <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")

#Apply Function to Each Day of the Week
lapply(days, render_function)
```

# Analysis for Each Day of the Week

The analysis for [Monday is available here](Monday-Report.md).

The analysis for [Tuesday is available here](Tuesday-Report.md).

The analysis for [Wednesday is available here](Wednesday-Report.md).

The analysis for [Thursday is available here](Thursday-Report.md).

The analysis for [Friday is available here](Friday-Report.md).

The analysis for [Saturday is available here](Saturday-Report.md).

The analysis for [Sunday is available here](Sunday-Report.md).